\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Joseph Norkplim Attah} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+233(050) 476-1981 \\ Ho, Volta Region, Ghana} 
\address{\href{mailto:josephattah005@gmail.com}{josephattah005@gmail.com} \\ \href{https://linkedin.com/in/joseph-attah-norkplim}{LinkedIn} \\ \href{https://github.com/Joe-Degs}{GitHub}}

\begin{document}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BSc in Human Settlement Planning}, Kwame Nkrumah University of Science and Technology \hfill {October 2022}\\
CWA: 63.90
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Javascript, Python, Go, Bash, SQL, C, SQL \\
Frameworks & Node.js, Express, Django, osmnx \\
Tools & Git, Docker, Kubernetes, GCP, Qemu, VirtualBox, Terraform, Vagrant, Linux, PostgreSQL, \\
&       QGIS \\
\\
Technical Skills & Systems and Network Programming, IP Networking, Virtualization, Automation, Documentation \\
Soft Skills & Time Management, Teamwork, Communication, Problem Solving, Leadership, Accountability
\\
\end{tabular}\\
\end{rSection}



%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{net} {python, Bash, Go net package, python socket module} \hfill \href{https://github.com/Joe-Degs/net}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a python module to make tcp, udp and unix socket programming easier.
    \item Wrote a detailed technical documentation with markdown.
    \item Utilized golang implementation as a guide increasing my understanding of Go's networking package and socket programming.
 \end{itemize}

\item \textbf{emulator} {Go, RISC-V, GCC} \hfill \href{https://github.com/Joe-Degs/emulator}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a RISC-V emulator capable of intepreting and executing the "rv64i" subset of the RISC-V ISA.
    \item Implemented the "rv64i" subset of RISC-V specification with a functional memory model and memory mapping unit.
    \item Utilized opensource technical documents from riscv.org as guide that increased my understanding of ISA's.
    \item Learned a great deal about cross compiling and how compilers worked.
 \end{itemize}

\item \textbf{autogis} {python, osmnx, OSM, QGIS} \hfill \href{https://github.com/Joe-Degs/AutoGIS/tree/master/test-thesis/autogis}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a tool to make visualizing and analysing street networks easier.
    \item Implemented functionality to geocode address and coordinates, plot street networks and visualize shortest path between two places.
    \item Utilized opensource tools, data and documentation which improved my understanding of urban data analytics and opensource mapping.
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	IT Support Personnel - Prempeh Library II ICT Center, KNUST.
\end{itemize}


\end{rSection}

%------------------------
% Use this more detailed section if you have Relevant work experience
% keep your resume to 1 page, if you need to remove a project to display relevant experience
% that is okay
% ----------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Intern Software Developer} \hfill December 2021 - February 2022\\
KoldChain \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Utilized the Django frameworks's testing tools to write test for models.
     \item Worked in a team improving team work and communication skills.
 \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

\end{rSection} 

% \begin{rSection}{Work History}
% \vspace{-1.25em}
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \end{rSection} 

%----------------------------------------------------------------------------------------



\end{document}